\section{Introduction}
\label{section:introduction}

	%\begin{draftlist}
		%\item Search-based and optimisation approaches to design are becoming more important (SBSE), but they are also important to adaptation (cite our cloud work,
					%mention robotics). 
		%\item The domains concerned can be quite complex, capturing them in traditional optimisation-oriented ways is difficult.
		%\item Some earlier work exists that tries to define a generic mechanism of translating models into genome representation (cite Crepe complete paper and
					%James' thesis), but this has issues. Discuss these issues in detail here or possibly in its own section below.
		%\item Main problem: loses lots of domain-specific knowledge.
		%\item We have spent lots of time to design a good meta-model based on extensive domain analysis. Why not use this knowledge when developing optimisations?
		%\item In this paper, we propose a technique and prototype tool for doing so and present its application to a simple case study. This forms the basis of a 
					%research agenda.
		%\item Structure of the paper etc.
	%\end{draftlist}

	Search-based software engineering (SBSE) is about using optimisation techniques for automating the search for (near-)optimal software designs \cite{HarmanJones01}.
	More recently, the use of search-based approaches has also been extended to software adaptation (e.g., \cite{Efstathiou+14,Chatziprimou+14}). Using search-based
	techniques allows the exploration of much larger design spaces than could be explored manually by developers. As a result, better solutions can be identified more
	quickly.
	
	However, as has been recognised before \cite{BurtonPoulding13,Kessentini+13}, the problem domains in software engineering are too complex to be effectively
	captured with traditional problem representations as they are typically used in search-based systems. Model-driven engineering (MDE) offers good techniques for
	capturing complex domains including their structural constraints by using meta-models. As a result, there has recently been increased interest in combining the
	advantages of SBSE and MDE \cite{Fleck+15,Drago+10,Drago+11,Drago+15,Efstathiou+14b,Williams13,Denil+14,Abdeen+14}.
	
	Much of this work has focused on finding good generic representations of models that are tailored towards the needs of standard optimisation algorithms (most
	typically, genetic algorithms, e.g. \cite{Deb+02}). As we will discuss in detail in Sect.~\ref{section:issues}, these generic encodings introduce their own
	challenges. Most importantly, they make it easy for search steps to produce invalid candidate solution; that is, models that do not satisfy the constraints
	expressed by the meta-model or its well-formedness rules.
	
	In this paper, we propose an alternative approach: instead of defining a secondary encoding for candidate solutions, we propose to run optimisation algorithms
	directly on models represented in standard meta-modelling data structures. We argue that given that developers have spent substantial time and effort designing
	meta-models that are a good representation of the domain, we should make use of as much of this information as possible during search and optimisation. We
	present a first prototype of a tool for running such optimisations and discuss some of the research challenges that need to be addressed to make this vision a
	reality.
	
	The remainder of this paper is structured as follows: In the next section, we give an overview of existing work defining generic approaches to SBSE in an MDE
	context. We then discuss some of the limitations of these existing works in Sect.~\ref{section:issues}, before presenting our own proposal in 
	Sect.~\ref{section:mde_optimisation}. Our work is only an initial exploration, highlighting more problems than providing definitive solutions, so in 
	Sect.~\ref{section:research_challenges}, we outline some of the key research challenges in this area.