\newif\ifdraft
\drafttrue
%\draftfalse

\ifdraft
	\documentclass[draft]{llncs}
	
	\usepackage{drafts}
\else
	\documentclass{llncs}

	\usepackage[nodrafts]{drafts}
\fi

\usepackage{figures}

\usepackage{hyperref}

\title{Towards Model-Based Optimisation: Using domain knowledge explicitly}

%\titlerunning{\draft{}}  % abbreviated title (for running head) also used for the TOC unless \toctitle is used

\author{Steffen Zschaler\inst{1}}
\institute{
	Department of Informatics\\
	King's College London\\
	\email{szschaler@acm.org}
}

\begin{document}

	\maketitle
	
	\begin{abstract}
		Search-based software engineering (SBSE) aims to treat soft\-ware-design problems as search and optimisation problems and address them by applying automated
		search and optimisation algorithms. A key concern is the adequate capture and representation of the structure of these design problems. Model-driven
		engineering (MDE) has a strong focus on domain-specific languages (DSLs) which are defined through meta-models, capturing the structure and constraints of a
		particular domain. There is, thus, a clear argument for combining both techniques to obtain the best of both worlds. Some authors have proposed a number of
		approaches in recent years, but these have mainly focused on the optimisation of transformations or on the identification of good generic encodings of models
		for search.
		%
		In this paper, we first provide a structured overview of the current state of the art before identifying limitations of the key proposals (transformation
		optimisation and generic genetic encodings of models). We then present a first prototype for running search algorithms directly on models themselves (rather
		than a separate representation) and derive key research challenges for this approach to model optimisation.
		
		\ifdraft
			\draft{To be submitted to MELO. max 12 pages, LNCS. Paper: April 18, 2016. Have permission to extend DL to April 22}
		\fi
		
		\keywords{evolutionary optimisation, object space, model-driven engineering, model transformations}
	\end{abstract}
	
	\input{introduction}
	
	\input{related_work}

	\input{issues}
	
	\input{mde_optimisation}	
	
	%\input{case_study}
	
	\input{research_challenges}
		
	\input{conclusions}
	
	\bibliographystyle{splncs}
	\bibliography{biblio}

\end{document}